Mixture distribution data generation

### 2022-02-04 Ch3_samplesize/ideafeb4.Rmd
Progress on my ideas.

>>>>

**What is the mathematical framework for this simulation?**  
First, we simulate a 'master' dataset which we assume to be the 'true' process

1.    Define the process used to generate animal movement  
2.    Define how to incorporate social group and individual variation  
3.    Establish any potential movement boundaries (max of 3000m in 15min from the data)  
4.    Generate seed dispersal kernels  
5.    Use Extreme values approach to describe the tail of seed dispersal kernels

Then, we design a sampling scheme.   
My hypothesis is that there will be a critical threshold, after which increasing the number of observations per individual won't matter to understand the tail of dispersal kernels, and we will benefit from sampling more individuals, instead of sampling fewer individuals with more observations.

1.    The sampling scheme should have this variation between individuals and number of observations per individual. *What are we sampling? locations?*  
2.
